Re-Examine Hybrid State-Space and Self-Attention for In-Context Learning

### 2025-01-28 paper.tex
Experiments: two subsection

\subsection{Datasets and Hyperparameters}
% 预训练数据集为包含 Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl 等开源数据集混合而成的数据集.
The pre-training dataset is a mixed dataset containing open-source datasets such as Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl, etc.

@@

\subsection{Associative Recall}
\label{sec:Associative_Recall}

% 我们在序列长度为 2048 的 80\% 的预训练数据集上训练了 1B 参数的 Jamba 模型与 1B 参数的 OTCE 模型,  然后将剩余的 20\% 的预训练数据集打包为 8K 上下文长度的数据集继续对模型进行预训练, 随后将微调数据集同样打包为 8K 上下文长度的数据集对模型进行微调, 将两个模型扩展到 8K 长度的上下文长度进行评估, 两个模型的参数设置如表~\ref{tab:associative_recall_params_zh} 所示.

>>>>

\subsection{Datasets and Hyperparameters}
% 预训练数据集为包含 Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl 等开源数据集混合而成的数据集.
The pre-training dataset is a mixed dataset containing open-source datasets such as Book~\cite{bookcrossing_dataset}, Wikipedia~\cite{wikipedia_dataset}, UNCorpus~\cite{uncorpus_dataset}, translation2019zh~\cite{translation2019zh_dataset}, WikiMatri~\cite{WikiMatri}, news-commentry~\cite{newscommentary_dataset}, ParaCrawlv9~\cite{paracrawl_dataset}, ClueCorpusSmall~\cite{cluecorpusSmall_dataset}, CSL~\cite{li-etal-2022-csl}, news-crawl~\cite{newscrawl_dataset}, etc.

@@
